---
title: "DefaultCreditCart"
author: "MojganAmiri"
date: "6/23/2020"
output:
  word_document: default
  html_document: default
---
##Read data set& Assign the header& rename our target variable 
```{r}

```




```{r}
uci_creditcard <- read.csv("C:\\Users\\yastr\\OneDrive\\Desktop\\creditcardclients.csv" , header = TRUE)
str(uci_creditcard)
colnames(uci_creditcard) <- unlist(uci_creditcard[1,])
uci_creditcard = uci_creditcard[-1, ]
head(uci_creditcard)
colnames(uci_creditcard)[colnames(uci_creditcard)=="default payment next month"] <- "default_payment"
```

## Convert to character then numeric(This is because factors are stored internally as integers with a table to give the factor level labels. Just using as.numeric will only give the internal integer codes.)
```{r}
uci_creditcard[, 1:25] <- sapply(uci_creditcard[, 1:25], as.character)
uci_creditcard[, 1:25] <- sapply(uci_creditcard[, 1:25], as.numeric)
str(uci_creditcard)
```
```{r}
install.packages("lazyeval")
install.packages("viridis")
install.packages("corrgram")
library(lazyeval)
library(corrgram)
corrgram(uci_creditcard, order=TRUE, lower.panel=panel.shade,
         upper.panel=panel.pie, text.panel=panel.txt,
         main="corrolation")
```
#correlation matrix &  find highly corolated feature 
```{r}
set.seed(7)
# load the library
library(mlbench)
library(caret)
correlationMatrix <- cor(uci_creditcard[,1:24])
# summarize the correlation matrix
print(correlationMatrix)
# find attributes that are highly corrected (ideally >0.75)
highlyCorrelated <- findCorrelation(correlationMatrix, cutoff=0.5)
# print indexes of highly correlated attributes
cat("column which are highly corrolated are :" ,highlyCorrelated)
```
#forward selection algorithm
```{r}
str(uci_creditcard)
library(MASS)
full <- lm(default_payment~LIMIT_BAL +SEX+ EDUCATION + MARRIAGE + 
                                  AGE +PAY_0+PAY_2+ PAY_3+PAY_4+PAY_5+PAY_6+BILL_AMT1+
                                  BILL_AMT2+BILL_AMT3+BILL_AMT4+BILL_AMT5+ BILL_AMT6+
                                  PAY_AMT1+PAY_AMT2+PAY_AMT3+PAY_AMT4+PAY_AMT5+PAY_AMT6,data=uci_creditcard)
null <- lm(default_payment~1,data=uci_creditcard)
stepF <- stepAIC(null, scope=list(lower=null, upper=full), direction= "forward", trace=TRUE)
summary(stepF)
```
#Backward selection algorithm
```{r}
full <- lm(default_payment~LIMIT_BAL +SEX+ EDUCATION + MARRIAGE + 
                                  AGE +PAY_0+PAY_2+ PAY_3+PAY_4+PAY_5+PAY_6+BILL_AMT1+
                                  BILL_AMT2+BILL_AMT3+BILL_AMT4+BILL_AMT5+ BILL_AMT6+
                                  PAY_AMT1+PAY_AMT2+PAY_AMT3+PAY_AMT4+PAY_AMT5+PAY_AMT6,data=uci_creditcard)
stepB <- stepAIC(full, direction= "backward", trace=TRUE)
summary(stepB)
```


# Convert Sex Data (1,2) with (Male, Female)
# Convert Education Level Data (0,1,2,3,4,5,6) with (Unknown, Graduate school, University, High school, Others, Unknown, Unknown)
# Convert Marriage level Data (0,1,2,3) with (Unknown, Married, Single, Others)
# Convert default.payment.next.month level Data (0,1) with (No, Yes)
# Convert Repayment Status columns to Factors
```{r}
uci_creditcard$SEX <- as.factor(uci_creditcard$SEX)
levels(uci_creditcard$SEX) <- c("Male","Female")

uci_creditcard$EDUCATION <- as.factor(uci_creditcard$EDUCATION)
levels(uci_creditcard$EDUCATION) <- c("Unknown", "Graduate School", "University", "High school", "Others", "Unknown", "Unknown")

uci_creditcard$MARRIAGE <- as.factor(uci_creditcard$MARRIAGE)
levels(uci_creditcard$MARRIAGE) <- c("Unknown" , "Married" , "Single" ,"Others")

uci_creditcard$default_payment <- as.factor(uci_creditcard$default_payment)
levels(uci_creditcard$default_payment) <- c("No" , "Yes")

uci_creditcard$PAY_0 <- as.factor(uci_creditcard$PAY_0)
uci_creditcard$PAY_2 <- as.factor(uci_creditcard$PAY_2)
uci_creditcard$PAY_3 <- as.factor(uci_creditcard$PAY_3)
uci_creditcard$PAY_4 <- as.factor(uci_creditcard$PAY_4)
uci_creditcard$PAY_5 <- as.factor(uci_creditcard$PAY_5)
uci_creditcard$PAY_6 <- as.factor(uci_creditcard$PAY_6)
```

# Summary data & Drop the ID Column & Check for Null value & dimantion of data
```{r}
summary(uci_creditcard)
uci_creditcard$ID <- NULL
sum(is.na(uci_creditcard))
dim(uci_creditcard)      
ncol(uci_creditcard)
nrow(uci_creditcard)

```
#distrubution of target value 
```{r}
library(ggplot2)
ggplot(uci_creditcard, aes(x=default_payment, fill = default_payment)) + 
  geom_bar() + 
  labs(title="Bar plot", 
       subtitle="Clients Grouped by Default Payment",
       caption="Source: UCI Credit Card",
       x="Default Payment",
       fill="Default Payment")
```



## Plot data using combination of demographic attributes
```{r}
library(gridExtra) 
graph1 <- ggplot(data=uci_creditcard, aes(x=SEX,fill=SEX)) + geom_bar() +
  labs(title = "Distribution by Gender", x ="Gender",fill = "Gender") +
  scale_fill_manual(values=c("#56B4E9", "#FF9999")) +
  theme(axis.text.x = element_text(angle = 45,hjust=1))

graph2 <- ggplot(data=uci_creditcard, aes(x=EDUCATION,fill=EDUCATION)) + geom_bar() +
  labs(title = "Distribution by Education Level", x ="Education Level",fill = "Education Level") +
  theme(axis.text.x = element_text(angle = 45,hjust=1))

graph3 <- ggplot(data=uci_creditcard, aes(x=MARRIAGE,fill=MARRIAGE)) + geom_bar() +
  labs(title = "Distribution by Marital Status", x ="Marital Status",fill = "Marital Status") +
  theme(axis.text.x = element_text(angle = 45,hjust=1))

grid.arrange(graph1,graph2,graph3,ncol=2)
```
# Plot data using combination of demographic attributes
```{r}

graph4 <- ggplot(data=uci_creditcard, aes(x=EDUCATION,fill=SEX)) + geom_bar(position='dodge') +
  labs(title = "Distribution by Education & Gender", x ="EDUCATION",fill = "GENDER") +
  scale_fill_manual(values=c("#56B4E9", "#FF9999")) +
  theme(axis.text.x = element_text(angle = 45,hjust=1))

graph5 <- ggplot(data=uci_creditcard, aes(x=MARRIAGE,fill=SEX)) + geom_bar(position='dodge') +
  labs(title = "Distribution by Marital Status & Gender", x ="Marital Status",fill = "Gender") +
  scale_fill_manual(values=c("#56B4E9", "#FF9999")) +
  theme(axis.text.x = element_text(angle = 45,hjust=1))

graph6 <- ggplot(data=uci_creditcard, aes(x=EDUCATION,fill=MARRIAGE)) + geom_bar(position='dodge') +
  labs(title = "Distribution by Education & Marital Status", x ="Education",fill = "Marital Status") +
  theme(axis.text.x = element_text(angle = 45,hjust=1))

grid.arrange(graph4, graph5, graph6,ncol=2)
```
#Plot SEX,LIMIT_BAL,EDUCATION VS default_payment
```{r}
graph7 <- ggplot(data=uci_creditcard, aes(x=SEX,fill=default_payment)) + geom_bar() +
  labs( x ="Gender",fill = "defualt") +
  scale_fill_manual(values=c("#56B4E9", "#FF9999")) +
  theme(axis.text.x = element_text(angle = 45,hjust=1))

graph8 <- ggplot(data=uci_creditcard, aes(x=LIMIT_BAL,fill=default_payment)) + geom_bar() +
  labs(title = " Non-Defaulter vs Defaulter within Specific Credit Limit Group", x ="limit",fill = "default_payment") +
  theme(axis.text.x = element_text(angle = 45,hjust=1))

graph9 <- ggplot(data=uci_creditcard, aes(x=EDUCATION,fill=default_payment)) + geom_bar() +
  labs(title = "Education vs Defaults Payments", x ="EDUCATION",fill = "default_payment") +
  theme(axis.text.x = element_text(angle = 45,hjust=1))
grid.arrange(graph7, graph8, graph9,ncol=2)
```
#Histogram PAY_X
```{r}
  pay.cols.names  <- paste0("PAY_", c(0, 2:6))

cols.to.factors <- c("SEX", "EDUCATION", "MARRIAGE", 
                     pay.cols.names, "default_payment")

uci_creditcard[cols.to.factors] <- lapply(uci_creditcard[cols.to.factors], factor)
library(ggplot2)
pay.histograms <- 
  lapply(pay.cols.names, 
         function (pay.col.name){ 
           ggplot(data = uci_creditcard[, pay.cols.names], 
                  aes(x = uci_creditcard[, pay.col.name])) +
             geom_bar(stat = "count") + 
             theme_minimal() +
             xlab(paste0("Repayment status ", pay.col.name)) +
             ylab("Observations count")
         })
pay.histograms
```
#histogram data
```{r}
a<-ggplot(data = uci_creditcard, aes(x = AGE)) + 
  geom_histogram(bins = 50, fill = "purple", col = "blue", alpha = 0.3) + 
  labs(title = "AGE")+ 
  scale_x_continuous(breaks = seq(min(0), max(90), by = 5), na.value = TRUE)


b<-ggplot(data = uci_creditcard, aes(x= BILL_AMT1)) + 
  geom_histogram(bins = 50, fill = "purple", col = "blue", alpha = 0.3) + 
  labs(title = "BILL_AMT1")+ 
  scale_x_continuous(breaks = seq(min(0), max(90), by = 5), na.value = TRUE)


c<-ggplot(data = uci_creditcard, aes(x= BILL_AMT2)) + 
  geom_histogram(bins = 50, fill = "purple", col = "blue", alpha = 0.3) + labs(title = "BILL_AMT2")+  
  scale_x_continuous(breaks = seq(min(0), max(90), by = 5), na.value = TRUE)

d<-ggplot(data = uci_creditcard, aes(x= BILL_AMT3)) + 
  geom_histogram(bins = 50, fill = "purple", col = "blue", alpha = 0.3) +  labs(title = "BILL_AMT3")+ 
  scale_x_continuous(breaks = seq(min(0), max(90), by = 5), na.value = TRUE)
grid.arrange(a, b,ncol=2)

e<-ggplot(data = uci_creditcard, aes(x= BILL_AMT4)) + 
  geom_histogram(bins = 50, fill = "purple", col = "blue", alpha = 0.3) + 
  scale_x_continuous(breaks = seq(min(0), max(90), by = 5), na.value = TRUE)


f<-ggplot(data = uci_creditcard, aes(x= BILL_AMT5)) + 
  geom_histogram(bins = 50, fill = "purple", col = "blue", alpha = 0.3) + 
  scale_x_continuous(breaks = seq(min(0), max(90), by = 5), na.value = TRUE)

grid.arrange(a,b,c,d,e,f,ncol=2)

g<-ggplot(data = uci_creditcard, aes(x= EDUCATION)) + 
  geom_histogram(bins = 50, fill = "purple", col = "blue", alpha = 0.3) + 
  scale_x_continuous(breaks = seq(min(0), max(90), by = 5), na.value = TRUE)
grid.arrange(a, b,ncol=2)

h<-ggplot(data = uci_creditcard, aes(x= LIMIT_BAL)) + 
  geom_histogram(bins = 50, fill = "purple", col = "blue", alpha = 0.3) + 
  scale_x_continuous(breaks = seq(min(0), max(90), by = 5), na.value = TRUE)
grid.arrange(a, b,ncol=2)

grid.arrange(a,b,c,d,e,f,ncol=2)
```


#Feature selection by using random forest
```{r}
data.partition<-sample(2,nrow(uci_creditcard),replace = TRUE,prob = c(0.75,0.25))
data.train<-uci_creditcard[data.partition==1,]
data.test<-uci_creditcard[data.partition==2,]


library(randomForest)
output.forest <- randomForest(default_payment~ LIMIT_BAL +SEX+ EDUCATION + MARRIAGE + 
                                  AGE +PAY_0 +PAY_2+ PAY_3+PAY_4+PAY_5+PAY_6+BILL_AMT1+
                                  BILL_AMT2+BILL_AMT3+BILL_AMT4+BILL_AMT5+ BILL_AMT6+
                                  PAY_AMT1+PAY_AMT2+PAY_AMT3+PAY_AMT4+PAY_AMT5+PAY_AMT6, data = data.train)



Import.vari<-importance(output.forest)
Import.vari
```

#implement models
```{r}
library(caret)
library(rpart)
library(rpart.plot)
library(rminer)
library(ggplot2)
library(Amelia)
library(nnet)
library(dummies)
library(caTools)
```
#according to corrrolation&highly corrolated feature &feature selection that has been done we will remove some attribute
```{r}
uci_creditcard$BILL_AMT6 <- NULL
uci_creditcard$BILL_AMT5<- NULL
uci_creditcard$BILL_AMT4<- NULL
uci_creditcard$BILL_AMT3<- NULL
uci_creditcard$BILL_AMT2<- NULL

uci_creditcard$PAY_2<- NULL
uci_creditcard$PAY_3<- NULL
uci_creditcard$PAY_4<- NULL
uci_creditcard$PAY_5<- NULL
uci_creditcard$PAY_6<- NULL
str(uci_creditcard)
```
#Normalize Data
```{r}
normalize <- function(x) {
               return ((x - min(x)) / (max(x) - min(x))) }

uci_creditcard1 <- as.data.frame(lapply(uci_creditcard[7:13], normalize))
uci_creditcard2 <- as.data.frame(lapply(uci_creditcard[1], normalize))
uci_creditcard3 <- as.data.frame(lapply(uci_creditcard[5], normalize))

uci_creditcard <- cbind(uci_creditcard2,uci_creditcard$SEX,uci_creditcard$EDUCATION,uci_creditcard$MARRIAGE,
                        uci_creditcard3,uci_creditcard$PAY_0,uci_creditcard1,uci_creditcard$default_payment)

colnames(uci_creditcard)[colnames(uci_creditcard)=="uci_creditcard$SEX"] <- "SEX"
colnames(uci_creditcard)[colnames(uci_creditcard)=="uci_creditcard$EDUCATION"] <- "EDUCATION"
colnames(uci_creditcard)[colnames(uci_creditcard)=="uci_creditcard$MARRIAGE"] <- "MARRIAGE"
colnames(uci_creditcard)[colnames(uci_creditcard)=="uci_creditcard$default_payment"] <- "default_payment"
colnames(uci_creditcard)[colnames(uci_creditcard)=="uci_creditcard$PAY_0"] <- "PAY_0"
str(uci_creditcard)
summary(uci_creditcard)
```


#Convert Factor level into dummy variable 
```{r}

SEX.dummies<-dummy(uci_creditcard$SEX,sep = '_')
EDUCATION.dummy<-dummy(uci_creditcard$EDUCATION,sep = '_')
MARRIAGE.dummy<-dummy(uci_creditcard$MARRIAGE,sep = '_')
PAY_0.dummies<-dummy(uci_creditcard$PAY_0,sep = '_')



uci_creditcard_clean<-cbind(uci_creditcard,MARRIAGE.dummy,SEX.dummies,EDUCATION.dummy,PAY_0.dummies)
dim(uci_creditcard_clean)
uci_creditcard_clean<-uci_creditcard_clean[,c(1,5,7:36)]
dim(uci_creditcard_clean)
str(uci_creditcard_clean)
```
#data partition
```{r}
uci_creditcard_clean_index <- sample(1:nrow(uci_creditcard_clean), 0.7 * nrow(uci_creditcard_clean))
train.set <- uci_creditcard_clean[uci_creditcard_clean_index ,]
test.set  <- uci_creditcard_clean[-uci_creditcard_clean_index ,]
dim(train.set)
dim(test.set)
str(test.set)
```
#Model1 Logistic Regression
```{r}
StartLG<-Sys.time()
log.model<-glm(default_payment~.,family = "binomial",train.set)
EndLG<-Sys.time()

summary(log.model)
#confint(log.model,level=.95)
default_predction<-predict(log.model,test.set,type='response')
#Generate ROC curve
model.AUC<-colAUC(default_predction,test.set$default_payment,plotROC = T)
abline(h=model.AUC,col='Green')
text(.2,.9,cex = .8,labels = paste("Optinonal Cutoff:",round(model.AUC,4)))

#Convert probabilities to class
default.class<-ifelse(default_predction>0.7651,1,0)

#transform back to factor for comparison
default.class<-factor(default.class)
test.set$default_payment<-factor(test.set$default_payment)

library(plyr)
test.set$default_payment <- revalue(test.set$default_payment, c("Yes"=1))
test.set$default_payment <- revalue(test.set$default_payment, c("No"=0))



#levels(as.factor(default.class))
#levels(as.factor(test.set$default_payment))

#Confusion Matrix
confusionMatrix(default.class,test.set$default_payment)

time<-EndLG-StartLG
cat("execution time is :",time )
```
####Second model Neural Network
```{r}
StartNN<-Sys.time()
NNlog<-multinom(default_payment~.,data = train.set)
EndNN<-Sys.time()

summary(NNlog)
#model Prediction
default_predction2<-predict(NNlog,test.set)
prediction.table<-table(default_predction2,test.set$default_payment)# put information into confusion matrix
prediction.table #print confusion matrix

#Correct Classifiction
sum(diag((prediction.table))/sum(prediction.table))
#Misclassification
1-sum(diag((prediction.table))/sum(prediction.table))

time<-EndNN-StartNN
cat("execution time is :",time )

```
#partition data and manipulate in diffrent way 
```{r}
uci_creditcard$default_paymentF<-factor(uci_creditcard$default_payment)
data.partition<-sample(2,nrow(uci_creditcard),replace = TRUE,prob = c(0.75,0.25))
data.train<-uci_creditcard[data.partition==1,]
data.test<-uci_creditcard[data.partition==2,]
 dim(data.test)
 str(uci_creditcard)
```
#Build Decision Tree
```{r}
StartDTree<-Sys.time()
d.tree<-rpart(data.train$default_paymentF~data.train$LIMIT_BAL+data.train$SEX+data.train$EDUCATION+data.train$MARRIAGE+
                data.train$PAY_0+data.train$BILL_AMT1+data.train$PAY_AMT6)
EndDTree<-Sys.time()

summary(d.tree)
#TO plot decision tree
rpart.plot(d.tree,extra = 3)

#default predict
tree.prediction<-predict(d.tree,data.train,type="class")

#to check levels
levels(tree.prediction)
levels(data.test$default_paymentF)

#Missclasification Matrix
confusionMatrix(tree.prediction,data.train$default_paymentF)

time<-EndDTree-StartDTree
cat("execution time is :",time )
```
#forth Random forest
```{r}
library(randomForest)
StartRFarest<-Sys.time()
output.forest <- randomForest(data.train$default_paymentF~data.train$LIMIT_BAL+data.train$SEX+data.train$EDUCATION+data.train$MARRIAGE+
                data.train$PAY_0+data.train$BILL_AMT1+data.train$PAY_AMT6,data = data.train)
EndRFarest<-Sys.time()

summary(output.forest)

random.prediction<-predict(output.forest,data.train,type="class")
levels(random.prediction)
levels(data.test$default_paymentF)
confusionMatrix(random.prediction,data.train$default_paymentF)
time<-EndRFarest-StartRFarest
cat("execution time is :",time )
```



